Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-28 paper/paper.tex
fix typo

  \item Section~\ref{disen} discusses \textbf{disentanglement}. In this part, we identify 
    different first-order datatypes which represent different layers of continuations, and
    disassemble their handlers into separate higher-order functions.

>>>>

  \item Section~\ref{disen} discusses \textbf{disentanglement}. In this part, we identify 
    different first-order datatypes which represent different layers of continuations, and
    disassemble their handlers into separate functions.
